Effort and Delay Discounting in a Foraging Environment

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
RT plot

We can see in the ECDFs below that most decisions to quit happened within the first second into the handling time. The reason why the physical and easy condition show slightly lagged responses is that the experiment allowed a one second grace period for participants to begin gripping. This results in some of them choosing to wait for that second to indicate an offer rejection.

``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# RTs
# let's try to do some survival curves
RTW <- unlist(lapply(waitData, function(data) {data$RT[data$Choice==0]})) # vector of all decision-related RTs for the wait group
RTC <- unlist(lapply(cogData, function(data) {data$`Choice RT`[data$Choice==0]})) # same for the cog group
RTP <- unlist(lapply(physData, function(data) {data$RT[data$Choice==0]}))
RTE <- unlist(lapply(easyData, function(data) {data$RT[data$Choice==0]}))

# create a data frame for plotting
RTgroups <- c(rep("Wait",length(RTW)), rep("Effort",length(RTC)), rep("Physical",length(RTP)), rep("Easy",length(RTE)))
RTall <- c(RTW,RTC,RTP,RTE)
RTframe <- data.frame(RTgroups, RTall)

# plot
ggplot(RTframe, aes(RTall, color = RTgroups)) + 
  stat_ecdf(lwd = 1) + 
  scale_color_manual(values = cols) + 
  scale_x_continuous(breaks = seq(14)) +
  labs(title = "ECDFs for the Response Times", x = "Seconds", y = "ECDF") +
  theme_classic()

# # and CIs for each (unnecessary unless I end up plotting)
# CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
# CIC <- median(CIC) - (quantile(CIC,0.025))
# CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
# CIW <- median(CIW) - (quantile(CIW,0.025))
# CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
# CIP <- median(CIP) - (quantile(CIP,0.025))
# CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
# CIE <- median(CIE) - (quantile(CIE,0.025))
# lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
# lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
# lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
# lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
# lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
# lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
# lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
# lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)

>>>>

The ECDF below shows the proportion of quits and acceptances occurring as the trial advanced. Drastic changes indicate the end of one of the possible handling times, and sccessful receipt of a reward. This shows that there were no quits during the handling time, and displays the proportion of acceptances (1 - the y axis here) for each cost at each handling/travel time combination. We can see in the ECDFs below that most decisions to quit happened within the first second into the handling time. The reason why the physical and easy condition show slightly lagged responses is that the experiment allowed a one second grace period for participants to begin gripping. This results in some of them choosing to wait for that second to indicate an offer rejection.

``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

# Proportion of forced travels per subject and cost type
propFails <- dataAll %>% 
  filter(Cost != "Wait") %>% 
  group_by(SubjID, Cost) %>% 
  summarise(propFails = mean(Choice == 2)) %>%
  group_by(Cost) %>% 
  summarise(meanQuit = mean(propFails))

# Reaction times ECDFs including offer and in-trial quits
(RTs <- dataAll %>%
  #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
  filter(Choice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
  ggplot(aes(RT, color = Cost)) + 
    stat_ecdf(lwd = 1.2) +
    geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
    scale_color_manual(values = cols) +
    scale_x_continuous(breaks = seq(14)) +
    theme(panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 16)))
